\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[margin=1in]{geometry}
\usepackage{array}
\usepackage{booktabs}
\usepackage{xcolor}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{microtype}
\usepackage{graphicx}
\usepackage{fancyhdr}

% Colors
\definecolor{cola}{RGB}{201,37,44}
\definecolor{colablack}{RGB}{0,0,0}
\definecolor{colasilvergray}{RGB}{193,193,193}

% Title format
\titleformat{\section}
  {\normalfont\Large\bfseries\color{cola}}
  {\thesection}{1em}{}
\titleformat{\subsection}
  {\normalfont\large\bfseries\color{cola}}
  {\thesubsection}{1em}{}

% Header and footer
\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{\textcolor{cola}{Coca-Cola-Inspired Beard Care}}
\fancyhead[R]{\textcolor{cola}{\thepage}}
\renewcommand{\headrulewidth}{1pt}
\renewcommand{\headrule}{\hbox to\headwidth{\color{cola}\leaders\hrule height \headrulewidth\hfill}}

\begin{document}

\begin{center}
\LARGE\textbf{\textcolor{cola}{Coca-Cola-Inspired Beard Care: Tonic and Balm}}
\end{center}

\vspace{1em}

This recipe page provides detailed instructions for crafting two complementary beard care products: a \textbf{Beard Tonic} and a \textbf{Vanilla Beard Balm}. Inspired by the iconic scent profile of Coca-Cola, these products work together to create a unique grooming experience. The tonic offers a light, fragrant conditioning effect, while the balm provides hold, moisture, and a deeper, resinous sweetness. Together, they capture the essence of cola's citrus-spice-resin character.

\vspace{1em}
\hrule
\vspace{1em}

\section*{Beard Tonic Recipe}

The beard tonic serves as a lightweight, fragrant base that mimics the sparkling, citrus-forward top notes of Coca-Cola. It provides light conditioning and a subtle scent lift, setting the stage for the balm's deeper, sweeter profile.

\subsection*{Ingredients}

\begin{center}
\begin{tabular}{p{4.5cm} p{2.5cm} p{8cm}}
\toprule
\textbf{Ingredient} & \textbf{Amount} & \textbf{Purpose} \\
\midrule
Frankincense Resin & 6 grams & Adds warm, balsamic depth and a resinous texture for light hold. \\
Myrrh Resin & 3 grams & Contributes earthy, slightly sweet notes and enhances shaping. \\
Glycerin & 250 microliters (0.25 ml) & Acts as a humectant to retain moisture and help dissolve resins. \\
Ethanol (95\% or higher) & \textasciitilde{}5.7 ml (adjust to 15 ml total) & Dissolves resins and essences; acts as a preservative. \\
Violet Leaf Absolute & 14.39 microliters & Provides a fresh, green, sparkling note to mimic cola's effervescence. \\
Bergamot Essential Oil & 300 microliters & Adds a bright, citrusy top note, echoing cola's orange and lime hints. \\
Neroli Essential Oil & 100 microliters & Contributes a floral, slightly citrusy middle note for complexity. \\
Coriander Essential Oil & 200 microliters & Offers a spicy, citrusy middle note, aligning with cola's spice blend. \\
Ceylon Cinnamon Essential Oil & 50 microliters & Provides a warm, spicy note reminiscent of cola's cinnamon undertone. \\
Nutmeg Absolute & 100 microliters & Delivers a rich, warm, spicy base note for depth. \\
Lime Essential Oil (Expressed) & 50 microliters & Adds a zesty, citrusy top note to enhance the cola-inspired freshness. \\
Ginger CO2 Extract & 10-15 microliters & Introduces a subtle, warm spice whisper for complexity. \\
Lemon Essential Oil (Organic) & 50 microliters & Adds a crisp, bright citrus note to complete the cola citrus trio. \\
\bottomrule
\end{tabular}
\end{center}

\subsection*{Instructions}

\begin{enumerate}[leftmargin=*]
\item \textbf{Prepare the Resins:}\\
   Grind 6 grams of frankincense and 3 grams of myrrh into a coarse powder using a mortar and pestle. This increases surface area for partial dissolution.

\item \textbf{Mix Resins with Glycerin:}\\
   Place the ground resins into a 15 ml glass bottle. Add 250 microliters (0.25 ml) of glycerin and shake well to moisten the resins.

\item \textbf{Prepare the Essence Mixture:}\\
   In a small container, combine the following using pipettes:
   \begin{itemize}
     \item Violet leaf absolute: 14.39 microliters
     \item Bergamot EO: 300 microliters
     \item Neroli EO: 100 microliters
     \item Coriander EO: 200 microliters
     \item Ceylon cinnamon EO: 50 microliters
     \item Nutmeg absolute: 100 microliters
     \item Lime EO: 50 microliters
     \item Ginger CO2: 10-15 microliters
     \item Lemon EO: 50 microliters
   \end{itemize}
   Stir gently to blend the essences.

\item \textbf{Combine with Ethanol:}\\
   Add \textasciitilde{}5.7 ml of ethanol to the essence mixture, adjusting to ensure the total liquid volume (ethanol + glycerin + essences) is approximately 6.764 ml. Stir or shake to incorporate.

\item \textbf{Add to Resins:}\\
   Pour the ethanol-essence mixture into the 15 ml bottle with resins and glycerin. If the liquid level is below 15 ml, top up with additional ethanol to reach 15 ml.

\item \textbf{Steep and Shake:}\\
   Cap the bottle and shake vigorously. Let it steep for at least 24 hours, shaking occasionally to aid dissolution.

\item \textbf{Optional Filtration:}\\
   For a clearer tonic, filter through a fine mesh or cheesecloth after steeping. Retaining sediment adds texture for light hold—your choice.
\end{enumerate}

\vspace{1em}
\hrule
\vspace{1em}

\section*{Vanilla Beard Balm Recipe}

The vanilla beard balm provides hold, deep conditioning, and a warm, resinous sweetness that complements the tonic's citrus-spice lift. It's designed to work synergistically with the tonic, creating a full Coca-Cola-inspired scent experience.

\subsection*{Ingredients}

\begin{center}
\begin{tabular}{p{4.5cm} p{2.5cm} p{8cm}}
\toprule
\textbf{Ingredient} & \textbf{Amount} & \textbf{Purpose} \\
\midrule
Carnauba Wax & 7 grams & Provides firm hold and heat stability for a long-lasting style. \\
Kokum Butter & 7 grams & Delivers deep conditioning with a non-greasy, matte finish. \\
Squalane (Olive-derived) & 10 grams & Acts as a lightweight, odorless carrier for easy application. \\
Vanilla Absolute & 120 microliters & Supplies the sweet, creamy backbone of the cola-inspired scent. \\
Frankincense Resin & 1 gram (ground fine) & Adds warm, resinous depth and slight tackiness for hold. \\
Myrrh Resin & 0.5 gram (ground fine) & Contributes earthy warmth to complement frankincense and vanilla. \\
Orange Blossom Absolute & 50 microliters & Introduces a floral, sweet-citrus middle note for complexity. \\
Tonka Bean 20\% Absolute & 50 microliters & Adds a sweet, vanilla-like warmth to enhance the base. \\
Benzoin Resinoid & 50 microliters & Provides a balsamic, sweet base note to tie into the resins. \\
Cardamom CO2 Extract & 10-15 microliters & Offers a subtle, warm spice whisper as a middle note. \\
\bottomrule
\end{tabular}
\end{center}

\subsection*{Instructions}

\begin{enumerate}[leftmargin=*]
\item \textbf{Prepare the Resins:}\\
   Grind 1 gram of frankincense and 0.5 gram of myrrh into a fine powder using a mortar and pestle.

\item \textbf{Melt the Base:}\\
   In a double boiler (or a pan with water and a heat-safe beaker), combine 7 grams of carnauba wax, 7 grams of kokum butter, and 10 grams of squalane. Heat gently until fully melted, stirring occasionally.

\item \textbf{Add Resins and Essences:}\\
   Stir the ground resins into the melted base. Then, add the following essences:
   \begin{itemize}
     \item Vanilla absolute: 120 microliters
     \item Orange blossom absolute: 50 microliters
     \item Tonka bean 20\% absolute: 50 microliters
     \item Benzoin resinoid: 50 microliters
     \item Cardamom CO2: 10-15 microliters
   \end{itemize}
   Mix thoroughly to ensure even distribution.

\item \textbf{Pour and Cool:}\\
   Remove from heat and pour the mixture into a 30 ml tin. Let it cool at room temperature until solid (about 1-2 hours).
\end{enumerate}

\vspace{1em}
\hrule
\vspace{1em}

\section*{Using the Tonic and Balm Together}

For the full Coca-Cola-inspired beard care experience:

\begin{enumerate}[leftmargin=*]
\item \textbf{Apply the Beard Tonic First:}\\
   Shake well and apply a few drops to your beard. Massage in for light conditioning and to introduce the sparkling, citrus-spice top notes.

\item \textbf{Follow with the Vanilla Beard Balm:}\\
   Warm a small amount of balm between your fingers and work it through your beard for hold, moisture, and the deeper, resinous sweetness.
\end{enumerate}

This combination creates a layered scent profile: the tonic's bright citrus and spice mimic cola's effervescence, while the balm's vanilla, resins, and subtle spice provide a warm, lingering finish—much like the depth of a classic cola.

\vspace{1em}
\hrule
\vspace{1em}

\section*{Scent Profile and Cola Inspiration}

\begin{itemize}
\item \textbf{Tonic:} The violet leaf, citrus (lime, bergamot, lemon), and spices (ginger, coriander, cinnamon, nutmeg) create a fresh, sparkling effect reminiscent of cola's initial fizz and citrus-spice burst.

\item \textbf{Balm:} Vanilla, orange blossom, tonka, benzoin, and cardamom add a warm, resinous sweetness that echoes cola's deeper, caramel-like undertones.
\end{itemize}

Together, these products offer a unique grooming experience that captures the essence of Coca-Cola while providing excellent beard care.

\end{document}